Datelife Reports

### 2020-06-11 paper_3-main.Rmd
missing references

Wide interest from the scientific community to make information from phylogenies in general and chronograms in particular available for consultation and reuse has spurred the creation of public platforms with various goals and characteristics. TreeBASE [@morell1996roots; @Piel2002], the Dryad repository (<http://datadryad.org/>), and the Open Tree of Life (OToL) repository [@Hinchliff2015; @mctavish2015phylesystem] are platforms that store and make available published phylogenies and chronograms for easy scientific reuse. Trees in all of them can be queried using automatised web procedures, which permit personalized, large scale searches that are also very fast.
OToL stores trees with branch length information from a wide range of living organisms, implementing a metadata structure that stores the branch length units (i.e., time or relative susbtitution rates). Treebase and Dryad repositories also contain trees from all groups of life, but the former did not store branch length information until recently (and lacks consistent metadata on what any branch lengths stored mean) and Dryad stores many other types of biological data using metadata that does not allow automatic distinction of types of trees and branch length units, impairing the automatised access to time of lineage divergence information.

>>>>

Wide interest from the scientific community to make information from phylogenies in general and chronograms in particular available for consultation and reuse has spurred the creation of public platforms with various goals and characteristics. TreeBASE [@piel2009treebase; @vos2012nexml], the Dryad repository (<http://datadryad.org/>), and the Open Tree of Life (OToL) repository [@Hinchliff2015; @mctavish2015phylesystem] are platforms that store and make available published phylogenies and chronograms for easy scientific reuse. Trees in all of them can be queried using automatised web procedures, which permit personalized, large scale searches that are also very fast.
OToL stores trees with branch length information from a wide range of living organisms, implementing a metadata structure that stores the branch length units (i.e., time or relative susbtitution rates). Treebase and Dryad repositories also contain trees from all groups of life, but the former did not store branch length information until recently (and lacks consistent metadata on what any branch lengths stored mean) and Dryad stores many other types of biological data using metadata that does not allow automatic distinction of types of trees and branch length units, impairing the automatised access to time of lineage divergence information.
